### 2020-03-09 README.Rmd
change from spread to pivot_wider

* `fit_bayesian_model()`. 
    + Inputs: `focal_and_comp`, `model_specs`
    + Output: `posterior_param`
* `predict_bayesian_model()`. 
    + Inputs: `focal_and_comp`, `model_specs`, `posterior_param`
    + Output: `focal_and_comp` with updated `growth_hat` variable
* Show observed vs predicted growth
* CV: `run_cv()` is a wrapper to `fit_bayesian_model()` and `predict_bayesian_model()`. 
* Permutation test:
  + Add line to that shuffles competitor species within `focal_and_comp` just before fitting model
  + permutation AND CV: add `run_shuffle` argument to `run_cv()`

>>>>

This output has the posterior parameters for the specified competition model. If `model_number = 1` this includes just the beta values for how focal tree DBH and identity affect growth. If `model_number = 2` it also includes a vector of lambdas for how total competitor basal area affect individuals of each group. If `model_number = 3` then lambda is a matrix which gives how individuals of each focal group respond to the competition of each competitor group. This `posterior_param` output can be used to get predicted growths for each individual (with `predict_bayesain_model`) to test how well the model performs. Or this `posterior_param` output can be plots (either the betas or lambdas) to understand what controls individual growth.

* `predict_bayesian_model()`. 
    + Inputs: `focal_and_comp`, `model_specs`, `posterior_param`
    + Output: `focal_and_comp` with updated `growth_hat` variable
* Show observed vs predicted growth
* CV: `run_cv()` is a wrapper to `fit_bayesian_model()` and `predict_bayesian_model()`. 
* Permutation test:
  + Add line to that shuffles competitor species within `focal_and_comp` just before fitting model
  + permutation AND CV: add `run_shuffle` argument to `run_cv()`
